---
title: "AK Clean GEE Vectors"
author: "Anna Talucci"
date: "2/16/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

What is included in this script:

Read in Alaska 2004 equal area vectors from GEE that were run on RdNBR and dNBR binary imagery. The input vectors recieved no geospatial processing in GEE beyond the delineation of vectors. 

Script below will clean and remove holes and add atttributes.


# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
```

# Projection

[Alaska Equal Area Conic](https://spatialreference.org/ref/esri/102006/)

+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs

```{r}
ea_ak = "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
```

# Read in shapefile

```{r}
dnbr = readOGR("../data/gee_fire_perimeters/2004_AK3338dNBR.shp", "2004_AK3338dNBR")
rdnbr = readOGR("../data/gee_fire_perimeters/2004_AK3338RdNBR.shp", "2004_AK3338RdNBR")

```

```{r}
plot(dnbr)
```

# Reproject in Equal area

```{r}
dnbr_ea = spTransform(dnbr, CRS(ea_ak))
rdnbr_ea = spTransform(rdnbr, CRS(ea_ak))
```

```{r}
dnbr_buff = gBuffer(dnbr_ea, width = 1000, capStyle="ROUND", joinStyle="ROUND")
rdnbr_buff = gBuffer(rdnbr_ea, width = 1000, capStyle="ROUND", joinStyle="ROUND")
```

# Remove holes inside polygons
```{r}
dnbr_nh = remove.holes(dnbr_buff)
rdnbr_nh = remove.holes(rdnbr_buff)
```

# Apply negative buffer
```{r}
dnbr_nbuf = gBuffer(dnbr_nh, width = -1000, capStyle="ROUND", joinStyle="ROUND")
rdnbr_nbuf = gBuffer(rdnb_nh, width = -1000, capStyle="ROUND", joinStyle="ROUND")
```

# Convert from sp to sf
```{r}
dnbr_sf = st_as_sf(dnbr_nbuf)
rdnbr_sf = st_as_sf(rdnbr_nbuf)
```

# Covert from Multipolygon to Polygon
```{r}
dnbr_cast = st_cast(dnbr_sf,"POLYGON")
rdnbr_cast = st_cast(rdnbr_sf,"POLYGON")
```


```{r}
dnbr_cast
```

```{r}
rdnbr_cast
```

# Create attributes
- ID based on row number
- area in meters squared, area_m
- area in Hectares, area_ha
- Year of the burn, fire_yr

```{r}
dnbr_at = dnbr_cast %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(dnbr_cast),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "dnbr") 

rdnbr_at = rdnbr_cast %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(rdnbr_cast),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "rdnbr") 
```


```{r}
head(dnbr_at$area_ha)
min(dnbr_at$area_ha)
max(dnbr_at$area_ha)
```

```{r}
head(rdnbr_at$area_ha)
min(rdnbr_at$area_ha)
max(rdnbr_at$area_ha)
```

```{r}
summary(dnbr_at)
summary(rdnbr_at)
```


# Remove polygons less than 400 ha
```{r}
dnbr_ha = filter(dnbr_at, as.numeric(dnbr_at$area_ha) >= 400)
rdnbr_ha = filter(rdnbr_at, as.numeric(rdnbr_at$area_ha) >= 400)

```

```{r}
summary(dnbr_ha)
summary(rdnbr_ha)
```

# Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(dnbr_ha, "../outputs/clean-shapefile/AK_EAdnbrFiresHa400_2004.shp", driver="ESRI Shapefile") 
st_write(rdnbr_ha, "../outputs/clean-shapefile/AK_EArdnbrFiresHa400_2004.shp", driver="ESRI Shapefile")  
```


