---
title: "Negative Buffer"
author: "Anna Talucci"
date: "3/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview

What is included in this script:

Read in Alaska 2004 vectors from GEE that were run on RdNBR and dNBR binary imagery. Script below will clean and remove holes and add atttributes.


# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
library(units)
library(smoothr)
```




# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```


[Alaska Equal Area Conic](https://spatialreference.org/ref/esri/102006/)

+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs

```{r}
ee_ak = "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
```


# Read in shapefile

```{r}
dnbr = readOGR("../data/gee_fire_perimeters/2004_AK_fires_dnbr.shp", "2004_AK_fires_dnbr")
rdnbr = readOGR("../data/gee_fire_perimeters/2004_AK_fires_rdnbr.shp", "2004_AK_fires_rdnbr")

```

```{r}
plot(dnbr)
```

# Reproject in Equal area

```{r}
dnbr_ee = spTransform(dnbr, CRS(ee_ak))
rdnbr_ee = spTransform(rdnbr, CRS(ee_ak))
```

# Remove holes inside polygons
```{r}
dnbr_nh = remove.holes(dnbr_ee)
rdnbr_nh = remove.holes(rdnbr_ee)
```

# Apply negative buffer

```{r}
dnbr_buf = gBuffer(dnbr_nh, width = -500, capStyle="ROUND", joinStyle="ROUND")
rdnbr_buf = gBuffer(rdnbr_nh, width = -500, capStyle="ROUND", joinStyle="ROUND")

```



# Convert from sp to sf
```{r}
dnbr_sf = st_as_sf(dnbr_buf)
rdnbr_sf = st_as_sf(rdnbr_buf)
```

# Covert from Multipolygon to Polygon

```{r}
dnbr_sf = st_cast(dnbr_sf,"POLYGON")
rdnbr_sf = st_cast(rdnbr_sf,"POLYGON")
```


```{r}
dim(dnbr_sf)
head(dnbr_sf)
```

```{r}
dim(rdnbr_sf)
head(rdnbr_sf)
```

# Create attributes
- ID based on row number
- area in meters squared, area_m
- area in Hectares, area_ha
- Year of the burn, fire_yr

```{r}
dnbr_at = dnbr_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(dnbr_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "dnbr") 

rdnbr_at = rdnbr_sf %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(rdnbr_sf),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "rdnbr") 
```


```{r}
head(dnbr_at$area_ha)
min(dnbr_at$area_ha)
max(dnbr_at$area_ha)
```

```{r}
head(rdnbr_at$area_ha)
min(rdnbr_at$area_ha)
max(rdnbr_at$area_ha)
```

```{r}
summary(dnbr_at)
summary(rdnbr_at)
```


# Remove polygons less than 400 ha
```{r}
dnbr_ha = filter(dnbr_at, as.numeric(dnbr_at$area_ha) >= 400)
rdnbr_ha = filter(rdnbr_at, as.numeric(rdnbr_at$area_ha) >= 400)

```

```{r}
summary(dnbr_ha)
summary(rdnbr_ha)
```

# Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(dnbr_ha, "../outputs/clean-shapefile/AK_dnbr_NegBuf_fires_2004.shp", driver="ESRI Shapefile") 
st_write(rdnbr_ha, "../outputs/clean-shapefile/AK_rdnbr_NegBuf_fire_2004.shp", driver="ESRI Shapefile")  
```


# Test Smoothing functions on polygons

See [Smooth and Tidy Spatial Features](https://cran.r-project.org/web/packages/smoothr/vignettes/smoothr.html)


```{r}
plot(dnbr_ha$geometry)
```

r_poly_smooth <- smooth(r_poly_filled, method = "ksmooth", smoothness = 2)
# plot
plot(rasterToPolygons(r), col = NA, border = NA) # set up plot extent
plot(r_poly_smooth, col = "#4DAF4A", border = "grey20", lwd = 1.5, add = TRUE)

```{r}
dnbr_ha_smooth <- smooth(dnbr_ha, method = "ksmooth", smoothness = 2)
```

```{r}
plot(dnbr_ha_smooth$geometry, col = "#4DAF4A", border = "grey20", lwd = 1.5)
```

```{r eval=FALSE, include=FALSE}
st_write(dnbr_ha_smooth, "../outputs/clean-shapefile/AK_dnbr_NegBuf_fires_2004_smooth.shp", driver="ESRI Shapefile")  
```

```{r}
dnbr_ha_smooth20 <- smooth(dnbr_ha, method = "ksmooth", smoothness = 20)
```

```{r}
plot(dnbr_ha_smooth20$geometry, col = "#4DAF4A", border = "grey20", lwd = 1.5)
```

```{r eval=FALSE, include=FALSE}
st_write(dnbr_ha_smooth20, "../outputs/clean-shapefile/AK_dnbr_NegBuf_fires_2004_smooth20.shp", driver="ESRI Shapefile")  
```