---
title: "Untitled"
author: "Anna Talucci"
date: "2/12/2021"
output: html_document
---


# Overview

for Alaska
Convert Hotspot/VIIRS point data to polygons. This is to limit the extent of the vector function in GEE to delinieate fire perimeters.


Data acquired from [FIRMS](https://firms.modaps.eosdis.nasa.gov/download/create.php)

Description of [Modis and VIIRS data](https://earthdata.nasa.gov/earth-observation-data/near-real-time/firms)

VIIRS launch October 2011, fire season data available 2012-present
MODIS launch    , available 2001-present

Take all annual hotspot data and make polygons 2001-2020, where 2012-2020 is the combine MODIS/VIIRS Data
 
What is included in this script:

Note:
Because these data sets area large spatial data sets, we will set this up to run annual data across each bounding box.
# Clear workspace

```{r}
rm(list=ls()) 
```
# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
library(lubridate)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

[Alaska Equal Area Conic](https://spatialreference.org/ref/esri/102006/)

+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs

```{r}
ee_ak = "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
```

# Data
## Bounding boxes
```{r}

ak_bbox = readOGR("../data/bbox/AK_bbox.shp", "AK_bbox")

```

## Hotspot Data (MODIS)
```{r}
usa_hs = readOGR("../data/2004_M6_USA/fire_archive_M6_2004.shp", "fire_archive_M6_2004") 
```

# Process subset USA to AK

## Covert to Equal Area
```{r}
ak_bbox_ee = spTransform(ak_bbox, CRS(ee_ak))
```

```{r}
usa_hs_ee = spTransform(usa_hs, CRS(ee_ak))
```

## Subset area to BBOX ecozone
```{r}
ak_hs = usa_hs_ee[ak_bbox_ee, ]
```

# Process point to polygon

## Buffer by 3k

```{r}
ak_hs_3k = gBuffer(ak_hs, width = 3000, capStyle="ROUND", joinStyle="ROUND")

```

### Remove holes in polygons
```{r}
ak_hs_3k_nh = remove.holes(ak_hs_3k)
```

### reproject to WGS for GEE
```{r}
ak_hs_wgs = spTransform(ak_hs_3k_nh, CRS( wgs_proj))

```


### Sp to sf

```{r}
ak_hs_wgs_sf = st_as_sf(ak_hs_wgs)
```

### Write to file
Create a shapefile

```{r eval=FALSE, include=FALSE}
st_write(ak_hs_wgs_sf, "../outputs/hotspot-polygon/hspoly_ak_2004.shp", driver="ESRI Shapefile")

```

