---
title: "Overlay GEE vectors with MTBS perimeters"
author: "Anna Talucci"
date: "2/16/2021"
output: html_document
---

# Overview

For comparing MTB to GEE vectors

Overlay to add attributes to pair fire perimeters (i.e., MTBS with GEE Vector dNBR or RdNBR)


# Library

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(readr)
library(cowplot)
library(ggcorrplot)
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(lubridate)
```
https://stackoverflow.com/questions/47784656/batch-load-shapefiles-from-directory-into-r

https://stackoverflow.com/questions/62419562/read-in-a-list-of-shapefiles-and-row-bind-them-in-r-preferably-using-tidy-synta
# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

"+proj=longlat +datum=NAD83 +no_defs"
```{r}
nad83 = "+proj=longlat +datum=NAD83 +no_defs"
```

[Alaska Equal Area Conic](https://spatialreference.org/ref/esri/102006/)

+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs

```{r}
ee_ak = "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
```

# Data
## MTBS Fire perimeters

```{r}
mtbs = st_read("../data/MTBS_Fires_2004/AK_Fires_2004.shp", "AK_Fires_2004")
```
## GEE Vectors

```{r}
dnbr = st_read("../data/clean-shapefile/AK_dnbr_fire_ha400_2004.shp", "AK_dnbr_fire_ha400_2004")
rdnbr = st_read("../data/clean-shapefile/AK_rdnbr_fire_ha400_2004.shp", "AK_rdnbr_fire_ha400_2004")
```


```{r}
dnbr_negbuf = st_read("../data/clean-shapefile/AK_dnbr_NegBuf_fires_2004.shp", "AK_dnbr_NegBuf_fires_2004")
rdnbr_negbuf = st_read("../data/clean-shapefile/AK_rdnbr_NegBuf_fire_2004.shp", "AK_rdnbr_NegBuf_fire_2004")
```


# Reproject

```{r}
st_crs(mtbs)$proj4string
```

```{r}
mtbs_ee = st_transform(mtbs, CRS(ee_ak))
```

```{r}
st_crs(mtbs_ee)$proj4string
```

# Look at attribute data
```{r}
head(mtbs_ee)
```

```{r}
min(mtbs_ee$GIS_ACRES)
max(mtbs_ee$GIS_ACRES)
```

```{r}

mtbs_ee_ha = mtbs_ee %>% dplyr::select(FIRE_YEAR:INCIDENT, MAP_METHOD, SOURCE:geometry) %>% dplyr::mutate(mtbs_area_m = round(st_area(mtbs_ee),1)) %>% dplyr::mutate(mtbs_area_ha = round(mtbs_area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "mtbs") 
```

```{r}
plot(mtbs_ee$geometry, col="red")
plot(dnbr$geometry, add=TRUE, col="blue")
```

## Polygon sizes
```{r}
min(mtbs_ee_ha$mtbs_area_ha)
max(mtbs_ee_ha$mtbs_area_ha)
```

```{r}
min(dnbr$area_ha)
max(dnbr$area_ha)
```

```{r}
min(dnbr_negbuf$area_ha)
max(dnbr_negbuf$area_ha)
```



```{r}
min(rdnbr$area_ha)
max(rdnbr$area_ha)
```

```{r}
min(rdnbr_negbuf$area_ha)
max(rdnbr_negbuf$area_ha)
```

# Summarize Datasets

## MTBS
```{r}
mtbs_ee_ha_df = mtbs_ee_ha %>% 
  mutate(mtbs_area_ha = as.numeric(mtbs_area_ha))
st_geometry(mtbs_ee_ha_df) <- NULL
```

```{r}
mtbs_ee_ha_df
```

```{r}
( mtbs_sum = mtbs_ee_ha_df %>% summarise(
n = n(),
Mean = mean(mtbs_area_ha),
SD = sd(mtbs_area_ha),
Median = median(mtbs_area_ha),
Minimum = min(mtbs_area_ha),
Maximum = max(mtbs_area_ha),
Total = sum(mtbs_area_ha))%>%
  mutate(index="mtbs"))
```

```{r}
( mtbs_400_sum = mtbs_ee_ha_df %>% 
    filter(mtbs_ee_ha_df$mtbs_area_ha >= 400) %>% 
    summarise(
n = n(),
Mean = mean(mtbs_area_ha),
SD = sd(mtbs_area_ha),
Median = median(mtbs_area_ha),
Minimum = min(mtbs_area_ha),
Maximum = max(mtbs_area_ha),
Total = sum(mtbs_area_ha))%>%
  mutate(index="mtbs_400"))
```

## dNBR
```{r}
dnbr_ee_ha_df = dnbr 
st_geometry(dnbr_ee_ha_df) <- NULL
```

```{r}
( dnbr_sum = dnbr_ee_ha_df %>% summarise(
n = n(),
Mean = mean(area_ha),
SD = sd(area_ha),
Median = median(area_ha),
Minimum = min(area_ha),
Maximum = max(area_ha),
Total = sum(area_ha)) %>%
  mutate(index="dnbr"))
```

## dNBR  negative buff
```{r}
dnbr_nb_df = dnbr_negbuf
st_geometry(dnbr_nb_df) <- NULL
```

```{r}
( dnbr_nb_sum = dnbr_nb_df %>% summarise(
n = n(),
Mean = mean(area_ha),
SD = sd(area_ha),
Median = median(area_ha),
Minimum = min(area_ha),
Maximum = max(area_ha),
Total = sum(area_ha)) %>%
  mutate(index="dnbr_nb"))
```

## RdNBR
```{r}
rdnbr_ee_ha_df = rdnbr 
st_geometry(rdnbr_ee_ha_df) <- NULL
```

```{r}
( rdnbr_sum = rdnbr_ee_ha_df %>% summarise(
n = n(),
Mean = mean(area_ha),
SD = sd(area_ha),
Median = median(area_ha),
Minimum = min(area_ha),
Maximum = max(area_ha),
Total = sum(area_ha)) %>%
  mutate(index="rdnbr"))
```

## dNBR  negative buff
```{r}
rdnbr_nb_df = rdnbr_negbuf
st_geometry(rdnbr_nb_df) <- NULL
```

```{r}
( rdnbr_nb_sum = rdnbr_nb_df %>% summarise(
n = n(),
Mean = mean(area_ha),
SD = sd(area_ha),
Median = median(area_ha),
Minimum = min(area_ha),
Maximum = max(area_ha),
Total = sum(area_ha)) %>%
  mutate(index="rdnbr_nb"))
```

## Combine Summaries

```{r}
sum_df = rbind(mtbs_sum, mtbs_400_sum, dnbr_sum, dnbr_nb_sum, rdnbr_sum, rdnbr_nb_sum)

sum_df
```


```{r eval=FALSE, include=FALSE}
write.csv(sum_df,  "../outputs/csv/2021-03-04_AK_summary_by_index.csv", row.names=FALSE)
```

# Rename columns for overlay
```{r}
summary(dnbr)
head(dnbr)
```

```{r}
dnbr = dnbr %>% rename(dnbr_ID = ID_obj, dnbr_area_m = area_m, dnbr_area_ha = area_ha, dnbr_fire_yr = fire_yr )
```

```{r}
summary(dnbr_negbuf)
head(dnbr_negbuf)
```

```{r}
dnbr_negbuf = dnbr_negbuf %>% rename(dnbr_nb_ID = ID_obj, dnbr_nb_area_m = area_m, dnbr_nb_area_ha = area_ha, dnbr_nb_fire_yr = fire_yr )
```

```{r}
summary(rdnbr)
head(rdnbr)
```

```{r}
rdnbr = rdnbr %>% rename(rdnbr_ID = ID_obj, rdnbr_area_m = area_m, rdnbr_area_ha = area_ha, rdnbr_fire_yr = fire_yr )
```

```{r}
summary(rdnbr_negbuf)
head(rdnbr_negbuf)
```

```{r}
rdnbr_negbuf = rdnbr_negbuf %>% rename( rdnbr_nb_ID = ID_obj, rdnbr_nb_area_m = area_m, rdnbr_nb_area_ha = area_ha, rdnbr_nb_fire_yr = fire_yr )
```

# Overlay

Overlay hotspot and  fire perimeter data by year in order to add attributes from hotspots to fire perimeters  that they interect. This will add attributes for:
- Fire start
- Fire end
- Accuracy



```{r}
head(mtbs_ee_ha)
```



## Process
sum_2001 = st_intersection(hotspot_2001, fire_2001) %>% sum_pt_poly()
```{r}
dnbr_mtbs = st_intersection(dnbr, mtbs_ee_ha)
rdnbr_dnbr_mtbs = st_intersection(rdnbr, dnbr_mtbs)
rdnbr_dnbr1_mtbs = st_intersection(dnbr_negbuf, rdnbr_dnbr_mtbs)
rdnbr1_dnbr1_mtbs = st_intersection(rdnbr_negbuf, rdnbr_dnbr1_mtbs)
```


```{r}
head(rdnbr1_dnbr1_mtbs)
```

```{r}
st_geometry(rdnbr1_dnbr1_mtbs) <- NULL
```
  mutate(dif_mtbs_dnbr = mtbs_area_ha - dnbr_area_ha) %>%
  mutate(dif_mtbs_rdnbr = mtbs_area_ha - rdnbr_area_ha)

```{r}
df_rdnbr_dnbr_mtbs = rdnbr1_dnbr1_mtbs %>% 
  dplyr::select(UNQEFIREID, MAP_METHOD, INCIDENT, mtbs_area_ha, dnbr_ID, dnbr_area_ha,  dnbr_nb_ID, dnbr_nb_area_ha, rdnbr_ID, rdnbr_area_ha, rdnbr_nb_ID, rdnbr_nb_area_ha) %>%
  mutate(mtbs_area_ha = as.numeric(mtbs_area_ha))

```

```{r}
head(df_rdnbr_dnbr_mtbs)
```


```{r eval=FALSE, include=FALSE}
write.csv(df_rdnbr_dnbr_mtbs,  "../outputs/csv/2021-03-03_AK_Perimeters_Compare.csv", row.names=FALSE)
```


# Calculate difference MTBS and GEE

Calculate differences between MTBS dnBR and GEE dNBR. 

```{r}
df_rdnbr_dnbr_mtbs %>% 
  dplyr::select(UNQEFIREID, MAP_METHOD, INCIDENT, mtbs_area_ha, dnbr_ID, dnbr_area_ha,  dnbr_nb_ID, dnbr_nb_area_ha) %>%
  mutate(mtbs_dnbrNB = (mtbs_area_ha - dnbr_nb_area_ha)) %>%
  mutate(mtbs_dnbr = (mtbs_area_ha - dnbr_area_ha))
```
## Filter for figure

```{r}
target <- c("Wall Street", "Chicken #1", "Anomaly", "Billy Creek", "Porcupine", "Upper Healy River", "North Dag", "Pingo", "Winter Tail")
```


filter(df, Ticker %in% target)

```{r}
mapped = df_rdnbr_dnbr_mtbs %>% 
  dplyr::select(UNQEFIREID, MAP_METHOD, INCIDENT, mtbs_area_ha, dnbr_ID, dnbr_area_ha,  dnbr_nb_ID, dnbr_nb_area_ha) %>%
  mutate(mtbs_dnbrNB = (mtbs_area_ha - dnbr_nb_area_ha)) %>%
  mutate(mtbs_dnbr = (mtbs_area_ha - dnbr_area_ha)) %>%
  filter(INCIDENT %in% target)

mapped
```


```{r eval=FALSE, include=FALSE}
write.csv(mapped,  "../outputs/csv/2021-03-05_AK_MappedFigure.csv", row.names=FALSE)
```

# Calculate difference 
f01_df = as.data.frame(f01)
Group  by MTBS fire events

  mutate(mtbs_dnbrNB = (mtbs_area_ha - dnbr_nb_area_ha)) %>%
  mutate(mtbs_dnbr = (mtbs_area_ha - dnbr_area_ha))
```{r}
df_rdnbr_dnbr_mtbs %>% 
  dplyr::select(UNQEFIREID, MAP_METHOD, INCIDENT, mtbs_area_ha, dnbr_ID, dnbr_area_ha,  dnbr_nb_ID, dnbr_nb_area_ha) %>% group_by(dnbr_ID)
```

```{r}
df_rdnbr_dnbr_mtbs %>% 
  dplyr::select(UNQEFIREID, MAP_METHOD, INCIDENT, mtbs_area_ha, dnbr_ID, dnbr_area_ha,  dnbr_nb_ID, dnbr_nb_area_ha) %>% 
  group_by(dnbr_ID)  %>%
  add_count(INCIDENT) %>%
  arrange(dnbr_nb_ID)

```


```{r}
df_rdnbr_dnbr_mtbs %>% 
  dplyr::select(UNQEFIREID, MAP_METHOD, INCIDENT, mtbs_area_ha, dnbr_ID, dnbr_area_ha,  dnbr_nb_ID, dnbr_nb_area_ha) %>% 
  group_by(dnbr_ID)  %>%
  add_count(INCIDENT) %>%
  arrange(dnbr_nb_ID)

```


