---
title: "Test ReduceToVector options from GEE"
author: "Anna Talucci"
date: "4/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

What is included in this script:

Read in Alaska 2004 vectors from GEE that were run on RdNBR and dNBR binary imagery. Script below will clean and remove holes and add atttributes.


# Packages

```{r include=FALSE}
library(sp)
library(sf)
library(rgdal) # geospatial data
library(raster)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(spatialEco)
library(units)
library(smoothr)
```




# Projections
[Alaska Equal Area Conic](https://spatialreference.org/ref/esri/102006/)

+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs

```{r}
ee_ak = "+proj=aea +lat_1=55 +lat_2=65 +lat_0=50 +lon_0=-154 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
```


# Read in shapefile

```{r}
opt1 = readOGR("../data/GEE/2004_mean30PolyFalseFalse.shp", "2004_mean30PolyFalseFalse")
opt2= readOGR("../data/GEE/2004_mean30PolyFalseTrue.shp", "2004_mean30PolyFalseTrue")
opt3= readOGR("../data/GEE/2004_mean30PolyTrueFalse.shp", "2004_mean30PolyTrueFalse")
```

```{r}
opt4 = readOGR("../data/GEE/2004_mean90PolyFalseFalse.shp", "2004_mean90PolyFalseFalse")
opt5= readOGR("../data/GEE/2004_mean90PolyFalseTrue.shp", "2004_mean90PolyFalseTrue")
opt6 = readOGR("../data/GEE/2004_mean90PolyTrueFalse.shp", "2004_mean90PolyTrueFalse")
```

# Reproject in Equal area

```{r}
opt1_ee = spTransform(opt1, CRS(ee_ak))
opt2_ee = spTransform(opt2, CRS(ee_ak))
opt3_ee = spTransform(opt3, CRS(ee_ak))
opt4_ee = spTransform(opt4, CRS(ee_ak))
opt5_ee = spTransform(opt5, CRS(ee_ak))
opt6_ee = spTransform(opt6, CRS(ee_ak))
```

#Buffer
```{r}
opt1_buff = st_buffer(opt1_ee, dist=1000, endCapStyle = "FLAT", joinStyle = "ROUND")
opt2_buff = st_buffer(opt2_ee, dist=1000, endCapStyle = "FLAT", joinStyle = "ROUND")
opt3_buff = st_buffer(opt3_ee, dist=1000, endCapStyle = "FLAT", joinStyle = "ROUND")
opt4_buff = st_buffer(opt4_ee, dist=1000, endCapStyle = "FLAT", joinStyle = "ROUND")
opt5_buff = st_buffer(opt5_ee, dist=1000, endCapStyle = "FLAT", joinStyle = "ROUND")
opt6_buff = st_buffer(opt6_ee, dist=1000, endCapStyle = "FLAT", joinStyle = "ROUND")
```


# Remove holes inside polygons
```{r}
opt1_nh = remove.holes(opt1_sp)
opt2_nh = remove.holes(opt2_sp)
opt3_nh = remove.holes(opt3_sp)
opt4_nh = remove.holes(opt4_sp)
opt5_nh = remove.holes(opt5_sp)
opt6_nh = remove.holes(opt6_sp)

```

# Apply negative buffer

```{r}
opt1_nbuf = gBuffer(opt1_nh, width = -1000, capStyle="ROUND", joinStyle="ROUND")
opt2_nbuf = gBuffer(opt2_nh, width = -1000, capStyle="ROUND", joinStyle="ROUND")
opt3_nbuf = gBuffer(opt3_nh, width = -1000, capStyle="ROUND", joinStyle="ROUND")
opt4_nbuf = gBuffer(opt4_nh, width = -1000, capStyle="ROUND", joinStyle="ROUND")
opt5_nbuf = gBuffer(opt5_nh, width = -1000, capStyle="ROUND", joinStyle="ROUND")
opt6_nbuf = gBuffer(opt6_nh, width = -1000, capStyle="ROUND", joinStyle="ROUND")

```



# Convert from sp to sf
```{r}
opt1_sf = st_as_sf(opt1_nbuf)
opt2_sf = st_as_sf(opt2_nbuf)
opt3_sf = st_as_sf(opt3_nbuf)
opt4_sf = st_as_sf(opt4_nbuf)
opt5_sf = st_as_sf(opt5_nbuf)
opt6_sf = st_as_sf(opt6_nbuf)

```

```{r}
plot(opt1_buff$geometry)
```

# Covert from Multipolygon to Polygon
all_shp_un = sf::st_union(all_shp)
```{r eval=FALSE, include=FALSE}
opt1_union = st_union(opt1_sf)
opt2_union = st_union(opt2_sf)
opt3_union = st_union(opt3_sf)
opt4_union = st_union(opt4_sf)
opt5_union = st_union(opt5_sf)
opt6_union = st_union(opt6_sf)

```

```{r eval=FALSE, include=FALSE}
opt1_cast = st_cast(opt1_union,"POLYGON")
opt2_cast = st_cast(opt2_union,"POLYGON")
opt3_cast = st_cast(opt3_union,"POLYGON")
opt4_cast = st_cast(opt4_union,"POLYGON")
opt5_cast = st_cast(opt5_union,"POLYGON")
opt6_cast = st_cast(opt6_union,"POLYGON")

```


```{r}
dim(opt1_cast)
dim(opt2_cast)
dim(opt3_cast)
dim(opt4_cast)
dim(opt5_cast)
dim(opt6_cast)

```

```{r}
head(opt1_cast)
head(opt2_cast)
head(opt3_cast)
head(opt4_cast)
head(opt5_cast)
head(opt6_cast)
```


# Create attributes
- ID based on row number
- area in meters squared, area_m
- area in Hectares, area_ha
- Year of the burn, fire_yr

```{r}
opt1_at = opt1_cast %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(opt1_cast),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "dnbr") 
```

```{r}
opt2_at = opt2_cast %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(opt2_cast),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "dnbr") 
```

```{r}
opt3_at = opt3_cast %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(opt3_cast),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "dnbr") 
```

```{r}
opt4_at = opt4_cast %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(opt4_cast),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "dnbr") 
```

```{r}
opt5_at = opt5_cast %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(opt5_cast),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "dnbr") 
```

```{r}
opt6_at = opt6_cast %>% dplyr::mutate(ID_obj = row_number()) %>% dplyr::mutate(area_m = round(st_area(opt6_cast),1)) %>% dplyr::mutate(area_ha = round(area_m*0.0001, 1)) %>% dplyr::mutate(fire_yr = 2004) %>% dplyr::mutate(index = "dnbr") 
```

```{r}
min(opt1_at$area_ha)
min(opt2_at$area_ha)
min(opt3_at$area_ha)
min(opt4_at$area_ha)
min(opt5_at$area_ha)
min(opt6_at$area_ha)
```

```{r}
max(opt1_at$area_ha)
max(opt2_at$area_ha)
max(opt3_at$area_ha)
max(opt4_at$area_ha)
max(opt5_at$area_ha)
max(opt6_at$area_ha)
```


# Remove polygons less than 400 ha
```{r}
opt1_ha = filter(opt1_at, as.numeric(opt1_at$area_ha) >= 400)
opt2_ha = filter(opt2_at, as.numeric(opt2_at$area_ha) >= 400)
opt3_ha = filter(opt3_at, as.numeric(opt3_at$area_ha) >= 400)
opt4_ha = filter(opt4_at, as.numeric(opt4_at$area_ha) >= 400)
opt5_ha = filter(opt5_at, as.numeric(opt5_at$area_ha) >= 400)
opt6_ha = filter(opt6_at, as.numeric(opt6_at$area_ha) >= 400)
```


# Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(opt1_ha, "../outputs/clean-shapefile/opt1.shp", driver="ESRI Shapefile") 
st_write(opt2_ha, "../outputs/clean-shapefile/opt2.shp", driver="ESRI Shapefile") 
st_write(opt3_ha, "../outputs/clean-shapefile/opt3.shp", driver="ESRI Shapefile") 
st_write(opt4_ha, "../outputs/clean-shapefile/opt4.shp", driver="ESRI Shapefile") 
st_write(opt5_ha, "../outputs/clean-shapefile/opt5.shp", driver="ESRI Shapefile") 
st_write(opt6_ha, "../outputs/clean-shapefile/opt6.shp", driver="ESRI Shapefile") 
```



# Test Smoothing functions on polygons

See [Smooth and Tidy Spatial Features](https://cran.r-project.org/web/packages/smoothr/vignettes/smoothr.html)


```{r}
plot(dnbr_ha$geometry)
```

r_poly_smooth <- smooth(r_poly_filled, method = "ksmooth", smoothness = 2)
# plot
plot(rasterToPolygons(r), col = NA, border = NA) # set up plot extent
plot(r_poly_smooth, col = "#4DAF4A", border = "grey20", lwd = 1.5, add = TRUE)

```{r}
dnbr_ha_smooth <- smooth(dnbr_ha, method = "ksmooth", smoothness = 2)
```

```{r}
plot(dnbr_ha_smooth$geometry, col = "#4DAF4A", border = "grey20", lwd = 1.5)
```

```{r eval=FALSE, include=FALSE}
st_write(dnbr_ha_smooth, "../outputs/clean-shapefile/AK_dnbr_NegBuf_fires_2004_smooth.shp", driver="ESRI Shapefile")  
```

```{r}
dnbr_ha_smooth20 <- smooth(dnbr_ha, method = "ksmooth", smoothness = 20)
```

```{r}
plot(dnbr_ha_smooth20$geometry, col = "#4DAF4A", border = "grey20", lwd = 1.5)
```

```{r eval=FALSE, include=FALSE}
st_write(dnbr_ha_smooth20, "../outputs/clean-shapefile/AK_dnbr_NegBuf_fires_2004_smooth20.shp", driver="ESRI Shapefile")  
```